Attributes-based Object Classification and Segmentation

### 2010-05-12 trunk/paper.tex
updated paper

%-------------------------------------------------------------------------------
% abstract
%-------------------------------------------------------------------------------
\begin{abstract}
Attributes have been shown to be effective in assisting object detection and
classification, and they provide means to also incorporate semantic
information available to and provided by humans.  On another front, the
combination of segmentation and object classification has been shown to
improve both segmentation and classification.  We present a method of incorporating
attributes into segmentation using a hierarchical methodology.
That is, using attributes as features, we discover attributes of regions
at all levels of a hierarchical segmentation,
incorporate hierarchical confidences in determining a confidence that
a given region is part of a given object, and segment the image using
these confidences.  We also present encouraging segmentation results
from experiments run using this method.
\end{abstract}

%-------------------------------------------------------------------------------
% introduction
%-------------------------------------------------------------------------------
\section{Introduction}
Very recent work on using attributes as features \cite{farhadi09, lampert09}
has shown that attributes are an effective way of communicating information
about an object in an image.  Attributes are, in essence, semantic high-level
features.  The attributes of an image are learned using low-level features,
and once learned, they can be used in object detection and also in describing
objects in an image that are unknown.

@@

\section{Object Detection and Segmentation}
\label{sec:detection}

@@

The object detection is based on the output of ADDITIVE\_PRUNE. If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, we think the object is detected in this image.

(We also plan to do the vertical confidence propogation. But due to the slowness of the experiment, we cannot incorporate it in this draft. We will show it in the final paper.)

@@

@@

As object detection is generally only as good as the features used, so also it
appears that this approach to segmentation is only as good as the attribute
selection and training.  We found that in images with poor segmentations, the
confidences in prediction of car attributes were generally low.  One problem
with this implementation of attribute classifiers was that we didn't use
the selection criterion described in \cite{farhadi09} that enhances within
category prediction ability.  This means that, for example, the wheel attribute
is highly similar to the car attribute and thus its discrimative ability
is hurt.  One future direction for this research would be to improve the attribute
training using the additional selection criterion and observe effects on
the segmentations.

>>>>

%-------------------------------------------------------------------------------
% abstract
%-------------------------------------------------------------------------------
\begin{abstract}
Attributes have been shown to be effective in assisting object classification and
classification, and they provide means to also incorporate semantic
information available to and provided by humans.  On another front, the
combination of segmentation and object classification has been shown to
improve both segmentation and classification.  We present a method of incorporating
attributes into segmentation using a hierarchical methodology.
That is, using attributes as features, we discover attributes of regions
at all levels of a hierarchical segmentation,
incorporate hierarchical confidences in determining a confidence that
a given region is part of a given object, and segment the image using
these confidences.  We also present encouraging segmentation results
from experiments run using this method.
\end{abstract}

%-------------------------------------------------------------------------------
% introduction
%-------------------------------------------------------------------------------
\section{Introduction}
Very recent work on using attributes as features \cite{farhadi09, lampert09}
has shown that attributes are an effective way of communicating information
about an object in an image.  Attributes are, in essence, semantic high-level
features.  The attributes of an image are learned using low-level features,
and once learned, they can be used in object classification and also in describing
objects in an image that are unknown.

@@

\section{Object Classification and Segmentation}
\label{sec:detection}

@@

The object classification is based on the output of ADDITIVE\_PRUNE. If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, we think the object is detected in this image.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/SubSegPrec.eps}
\caption{Graph of the precision of the subtractive segmentation
algorithm against confidence, or attribute similarity.  Despite
the noise, there is an upward trend in the precision
as the similarity score increases, as shown by the 
quadratic least-squares fit.}
\label{fig:sub_seg_prec}
\end{figure}

@@

As object classification is generally only as good as the features used, so also it
appears that this approach to segmentation is only as good as the attribute
selection and training.  We found that in images with poor segmentations, the
confidences in prediction of car attributes were generally low.  One problem
with this implementation of attribute classifiers was that we didn't use
the selection criterion described in \cite{farhadi09} that enhances within
category prediction ability.  This means that, for example, the wheel attribute
is highly similar to the car attribute and thus its discrimative ability
is hurt.  One future direction for this research would be to improve the attribute
training using the additional selection criterion and observe effects on
the segmentations.
